Changes in accessibility to food banks and food services during COVID-19 and implications for low income populations in Hamilton, Ontario

### 2021-08-27 Accessibility-Foodbanks-Hamilton/Accessibility-Foodbanks-Hamilton-abstract.Rmd
Updated abstract in title page and abstract file

---
title: "Changes in accessibility to food banks and food services during COVID-19 and implications for low income populations in Hamilton, Ontario"
author:
  - name: Author One
    email: author1@example.com
    affiliation: Some University
  - name: Author Two
    email: author2@example.com
    affiliation: Another University
    footnote: 1
  - name: Author Three
    email: author3@example.com
    affiliation: Some University
  - name: Author Four
    email: author4@example.com
    affiliation: Some University
address:
  - code: Some University
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  In this paper we analyze the changes in accessibility to food banks and related services before and during the COVID-19 pandemic in the City of Hamilton, Ontario. Food banks and services are the last line of support for households facing food insecurity; as such, their relevance cannot be ignored in the midst of the economic upheaval caused by the pandemic. Our analysis is based on the application of balanced floating catchment areas, and concentrates on households with lower incomes (<CAD40,000, approximately the Low Income Cutoff Value for a city of Hamilton's size). We find that accessibility was low to begin with in suburban and exurban parts of the city; furthermore, about 14\% of locations originally available in Hamilton closed during the pandemic, further reducing accessibility. The impact of closures on the level of service of the remaining facilities, and on accessibility, was disproportionate, with system-wide losses exceeding 40\%. Those losses were geographically and demographically uneven. While every part of the city faced a reduction in accessibility, inner suburbs fared worse in terms of loss of accessibility. As well, children (age $\le 18$) appear to have been impacted the most.

>>>>

---
title: "Changes in accessibility to food banks and food services during COVID-19 and implications for low income populations in Hamilton, Ontario"
author:
  - name: Author One
    email: author1@example.com
    affiliation: Some University
  - name: Author Two
    email: author2@example.com
    affiliation: Another University
    footnote: 1
  - name: Author Three
    email: author3@example.com
    affiliation: Some University
  - name: Author Four
    email: author4@example.com
    affiliation: Some University
address:
  - code: Some University
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  In this paper we analyze the changes in accessibility to community and emergency food services before and during the COVID-19 pandemic in the City of Hamilton, Ontario. Many of these food services are the last line of support for households facing food insecurity; as such, their relevance cannot be ignored in the midst of the economic upheaval caused by the pandemic. Our analysis is based on the application of balanced floating catchment areas and concentrates on households with lower incomes (<CAD40,000, approximately the Low Income Cutoff Value for a city of Hamilton's size). We find that accessibility was low to begin with in suburban and exurban parts of the city; furthermore, about 14\% of locations originally available in Hamilton closed during the pandemic, further reducing accessibility. The impact of closures on the level of service of the remaining facilities, and on accessibility, was disproportionate, with system-wide losses exceeding 40\%. Those losses were geographically and demographically uneven. While every part of the city faced a reduction in accessibility, inner suburbs fared worse in terms of loss of accessibility. As well, children (age $\le 18$) appear to have been impacted the most.

### 2021-08-27 Accessibility-Foodbanks-Hamilton/Accessibility-Foodbanks-Hamilton-title-page.Rmd
Updated abstract in title page and abstract file

---
title: "Changes in accessibility to food banks and food services during COVID-19 and implications for low income populations in Hamilton, Ontario"
author:
  - name: Christopher D. Higgins
    email: cd.higgins@utoronto.ca
    affiliation: University of Toronto Scarborough
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
    footnote: 1
  - name: Gyoorie Kim
    email: gyoorie.kim@mail.utoronto.ca
    affiliation: University of Toronto Mississauga
  - name: Jue Wang
    email: gis.wang@utoronto.ca
    affiliation: University of Toronto Mississauga
address:
  - code: University of Toronto Scarborough
    address: Department of Geography & Planning, University of Toronto Scarborough, 1265 Military Trail, Toronto, ON M1C1A4
  - code: McMaster University
    address: School of Earth, Environment and Society, McMaster University, Hamilton, ON, L8S 4K1, Canada
  - code: University of Toronto Mississauga
    address: Department of Geography, Geomatics and Environment, University of Toronto Mississauga, 3359 Mississauga Road, Mississauga, ON, L5L 1C6 , Canada   
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  In this paper we analyze the changes in accessibility to food banks and related services before and during the COVID-19 pandemic in the City of Hamilton, Ontario. Food banks and services are the last line of support for households facing food insecurity; as such, their relevance cannot be ignored in the midst of the economic upheaval caused by the pandemic. Our analysis is based on the application of balanced floating catchment areas, and concentrates on households with lower incomes (<CAD40,000, approximately the Low Income Cutoff Value for a city of Hamilton's size). We find that accessibility was low to begin with in suburban and exurban parts of the city; furthermore, about 14\% of locations originally available in Hamilton closed during the pandemic, further reducing accessibility. The impact of closures on the level of service of the remaining facilities, and on accessibility, was disproportionate, with system-wide losses exceeding 40\%. Those losses were geographically and demographically uneven. While every part of the city faced a reduction in accessibility, inner suburbs fared worse in terms of loss of accessibility. As well, children (age $\le 18$) appear to have been impacted the most.

>>>>

---
title: "Changes in accessibility to food banks and food services during COVID-19 and implications for low income populations in Hamilton, Ontario"
author:
  - name: Christopher D. Higgins
    email: cd.higgins@utoronto.ca
    affiliation: University of Toronto Scarborough
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
    footnote: 1
  - name: Gyoorie Kim
    email: gyoorie.kim@mail.utoronto.ca
    affiliation: University of Toronto Mississauga
  - name: Jue Wang
    email: gis.wang@utoronto.ca
    affiliation: University of Toronto Mississauga
address:
  - code: University of Toronto Scarborough
    address: Department of Geography & Planning, University of Toronto Scarborough, 1265 Military Trail, Toronto, ON M1C1A4
  - code: McMaster University
    address: School of Earth, Environment and Society, McMaster University, Hamilton, ON, L8S 4K1, Canada
  - code: University of Toronto Mississauga
    address: Department of Geography, Geomatics and Environment, University of Toronto Mississauga, 3359 Mississauga Road, Mississauga, ON, L5L 1C6 , Canada   
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  In this paper we analyze the changes in accessibility to community and emergency food services before and during the COVID-19 pandemic in the City of Hamilton, Ontario. Many of these food services are the last line of support for households facing food insecurity; as such, their relevance cannot be ignored in the midst of the economic upheaval caused by the pandemic. Our analysis is based on the application of balanced floating catchment areas and concentrates on households with lower incomes (<CAD40,000, approximately the Low Income Cutoff Value for a city of Hamilton's size). We find that accessibility was low to begin with in suburban and exurban parts of the city; furthermore, about 14\% of locations originally available in Hamilton closed during the pandemic, further reducing accessibility. The impact of closures on the level of service of the remaining facilities, and on accessibility, was disproportionate, with system-wide losses exceeding 40\%. Those losses were geographically and demographically uneven. While every part of the city faced a reduction in accessibility, inner suburbs fared worse in terms of loss of accessibility. As well, children (age $\le 18$) appear to have been impacted the most.
